---
title: "Issues to calculate sensitivity and specificity of GWA studies"
author: "Jose Alquicira Hernandez"
date: "11/05/2015"
output: html_document
---
```{r open file, echo=FALSE}
library('knitr')
setwd("/home/joseah/Documents/jeff_leek_lab/github/GWASanalysis/exploratory_data_analysis")
columns <- c("PUBMEDID", "LINK", "STUDY", "DISEASE.TRAIT", "INITIAL.SAMPLE.DESCRIPTION", "REPLICATION.SAMPLE.DESCRIPTION", "STRONGEST.SNP_RISK.ALLELE",
             "SNPS", "RISK.ALLELE.FREQUENCY", "P-VALUE", "ORorBETA")

assoc <- read.table("phenotypes_to_study_w_required_data", sep = "\t", 
                    col.names = columns, quote = "", comment.char = "", stringsAsFactors = FALSE)
assoc <- assoc[order(assoc$DISEASE.TRAIT),]
rownames(assoc) <- paste(seq_len(nrow(assoc)), assoc$SNPS, sep = "_")
assoc$CASES <- NA
assoc$CONTROLS <- NA
assoc$STAGE <- NA
assoc$CLINICAL.VARIABLES <- NA
assoc$NOTES <- NA
assoc$Sensitivity <- NA
assoc$Specificity <- NA
assoc$A <- NA
assoc$B <- NA
assoc$C <- NA
assoc$D <- NA
```

```{r echo=FALSE}
SenSes <- function(studies){
    n_cases <- studies$CASES
    n_controls <- studies$CONTROLS
    RAF <- studies$RISK.ALLELE.FREQUENCY
    OR <- studies$ORorBETA
    b <- n_controls * RAF
    d <- n_controls - b
    a <- b*n_cases/((d/OR) + b)
    c <- n_cases - a
    Sensitivity = a/(a+c)
    Specificity = d/(b+d)
    return(list(Sensitivity = Sensitivity, 
                Specificity = Specificity, 
                A = round(a),
                B = round(b),
                C = round(c),
                D = round(d)))
}

contingency_table <- function(snp){
    cont_table <-matrix(snp[c("A", "C","CASES", "B", "D", "CONTROLS")], 
                        nrow = 3, 
                        dimnames = list(c(paste(unlist(strsplit(snp$STRONGEST.SNP_RISK.ALLELE, "-"))[2], "(+)"), 
                                          paste(unlist(strsplit(snp$STRONGEST.SNP_RISK.ALLELE, "-"))[2], "( - )"), 
                                          "Total"), 
                                        c("Cases", "Controls"))
                        )
    
    kable(cont_table)
    }

```

---

```{r results = 'asis', echo=FALSE}
i <- 2
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
```

### Populations: Cases and controls

```{r results='asis', echo = FALSE}
file <- paste0("'", './images_evidence/', snp[,1],".png", "'")
cat("<img src=",file,"/>")

```


Sum of cases and controls for initial and replication sample:

```{r echo=FALSE}
cases = 844 + 1547
controls = 1255 + 1209

```

N째 Cases = `r cases`

N째 Controls = `r controls`

The number of cases and controls to be considered will be the ones reported in the previous table.

```{r echo=FALSE}
snp$CASES <- 2449
snp$CONTROLS <- 2561 

```

__N째 Cases = `r snp$CASES`__

__N째 Controls = `r snp$CONTROLS`__

### Risk allele frequency
The risk allele frequency is the same in the paper.


```{r results='asis', echo = FALSE}
snp$STAGE <- "1+2 | combined"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- NA
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

---

```{r results = 'asis', echo=FALSE}
i = 3
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
```


### Populations: Cases and controls
```{r results='asis', echo = FALSE}
file <- paste0("'", './images_evidence/', snp[,1],".png", "'")
cat("<img src=",file,"/>")
```


### Risk allele frequency
The MAF for the first phase is reported for this SNP, but the RAF for the combined phase does not. We will consider the sample size for controls and cases from the first phase: 3941 cases and 7848 controls and the corresponding odd ratio 1/0.84 = `r 1/0.84`. The MAF reported corresponds in the paper corresponds to the minor allele in controls, so RAF in the catalog will be preserved. 


```{r results='asis', echo = FALSE}
snp$P.VALUE <- 1e-09
snp$ORorBETA <- round(1/0.84, 2)
snp$CASES <- 3941
snp$CONTROLS <- 7848
snp$STAGE <- "1"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "Heritability of up to 76% for Alzheimer's disease | Flipped odd ratio | Population attributable risk reported"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

The same assumptions are considerated for the remaining SNPs of this study.

```{r results = 'asis', echo=FALSE}
i = 4
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
```

```{r results='asis', echo = FALSE}
snp$CASES <- 3941
snp$CONTROLS <- 7848 
snp$STAGE <- "1"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "Heritability of up to 76% for Alzheimer's disease | Population attributable risk reported"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

```{r results = 'asis', echo=FALSE}
i = 5
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
```

```{r results='asis', echo = FALSE}
snp$P.VALUE <- 2e-08
snp$ORorBETA <- round(1/0.85, 2)
snp$CASES <- 3941
snp$CONTROLS <- 7848 
snp$STAGE <- "1"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "Heritability of up to 76% for Alzheimer's disease | Flipped odd-ratio | Population attributable risk reported"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

---

```{r results = 'asis', echo=FALSE}
i = 6
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
```


### Populations: Cases and controls
```{r results='asis', echo = FALSE}
file <- paste0("'", './images_evidence/', snp[,1],".png", "'")
cat("<img src=",file,"/>")
```

Sample sizes for cases and controls differ from the ones reported in the catalog.

### Risk allele frequency

The RAF and odd ratio reported are not consistent with the catalog.

Therefore, we will use the data provided by the paper for the combined stage (1+2)


```{r results='asis', echo = FALSE}
snp$P.VALUE <- 8e-09
snp$RISK.ALLELE.FREQUENCY <- 1 - 0.38
snp$ORorBETA <- round(1/0.86, 2)
snp$CASES <- 5791
snp$CONTROLS <- 8420
snp$STAGE <- "1+2 | combined"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "Stratified analysis by populations: Belgium, Finland, Italy and Spain | flipped odd ratio"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

For the remaining SNPs, the same criteria will be used.

```{r results = 'asis', echo=FALSE}
i = 7
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
snp$P.VALUE <- 9e-09
snp$RISK.ALLELE.FREQUENCY <- 1 - 0.41
snp$ORorBETA <- round(1/0.86, 2)
snp$CASES <- 5828
snp$CONTROLS <- 8425
snp$STAGE <- "1+2 | combined"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "Stratified analysis by populations: Belgium, Finland, Italy and Spain | flipped odd ratio | haplotype analysis not considered for this SNP, just association analysis in CLU locus"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

```{r results = 'asis', echo=FALSE}
i = 8
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
```

```{r results='asis', echo = FALSE}
file <- paste0("'", './images_evidence/', snp[,1],"_2.png", "'")
cat("<img src=",file,"/>")
```

```{r results = 'asis', echo=FALSE}
snp$P.VALUE <- 9e-08
snp$RISK.ALLELE.FREQUENCY <- 0.19
snp$ORorBETA <- 1.19
snp$CASES <- 5735
snp$CONTROLS <- 8418
snp$STAGE <- "1+2 | combined"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "Stratified analysis by populations: Belgium, Finland, Italy and Spain | haplotype analysis not considered for this SNP, just association analysis in CR1 locus"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

```{r results = 'asis', echo=FALSE}
i = 9
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
snp$P.VALUE <- 4e-09
snp$RISK.ALLELE.FREQUENCY <- 0.19
snp$ORorBETA <- 1.21
snp$CASES <- 5905
snp$CONTROLS <- 8526
snp$STAGE <- "1+2 | combined"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "Stratified analysis by populations: Belgium, Finland, Italy and Spain | haplotype analysis not considered for this SNP, just association analysis in CR1 locus"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

```{r results = 'asis', echo=FALSE}
i = 10
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
snp$P.VALUE <- 9e-08
snp$RISK.ALLELE.FREQUENCY <- 0.28
snp$ORorBETA <- 1.16
snp$CASES <- 5887
snp$CONTROLS <- 8508
snp$STAGE <- "1+2 | combined"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "Stratified analysis by populations: Belgium, Finland, Italy and Spain | haplotype analysis not considered for this SNP, just association analysis in CLU locus"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

---

```{r results = 'asis', echo=FALSE}
i = 32
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
file <- paste0("'", './images_evidence/', snp[,1],".png", "'")
cat("<img src=",file,"/>") 
snp$CASES <- 4533
snp$CONTROLS <- 17513
snp$STAGE <- "Combined"
snp$CLINICAL.VARIABLES <- "Pathological breast cancer subtypes: Estrogen receptor, progesterone receptor, histopathology(ductal, lobular, ductal vs. lobular), stage, grade"
snp$NOTES <- "Stratified analysis from multiethnic cohort: European Americans, Latinas, Hawaiians, Japanese, African Americans | Allelic interaction analysis"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

```{r results = 'asis', echo=FALSE}
i = 33
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
file <- paste0("'", './images_evidence/', snp[,1], "_", snp[,8],".png", "'")
cat("<img src=",file,"/>") 
snp$CASES <- 4554
snp$CONTROLS <- 17577
snp$STAGE <- "Combined"
snp$CLINICAL.VARIABLES <- "Pathological breast cancer subtypes: Estrogen receptor, progesterone receptor, histopathology(ductal, lobular, ductal vs. lobular), stage, grade"
snp$NOTES <- "Stratified analysis from multiethnic cohort: European Americans, Latinas, Hawaiians, Japanese, African Americans | Allelic interaction analysis"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

---

```{r results = 'asis', echo=FALSE}
i = 34
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
file <- paste0("'", './images_evidence/', snp[,1],".png", "'")
cat("<img src=",file,"/>")
    snp$CASES <- 249 + 950 + 243
    snp$CONTROLS <- 299 + 979 + 187
    snp$STAGE <- "1+2+3 | combined"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- NA
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

---

```{r results = 'asis', echo=FALSE}
i = 35
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
file <- paste0("'", './images_evidence/', snp[,1],".png", "'")
cat("<img src=",file,"/>")
# snp$RISK.ALLELE.FREQUENCY <- 3962 - (1812/2 + 536)
snp$CASES <- 6472
snp$CONTROLS <- 3962
snp$STAGE <- "1+2+3 | combined"
snp$CLINICAL.VARIABLES <- "Age | Education | Age at menarche | Postmenopausal (%) | Age at menopause | Number of Live Births | Age at first live birth | Used HRT-Hormone replacement therapy (%) | Breast cancer family history | Prior BBD diagnosis| Body mass index | Waist-to-hip ratio"
snp$NOTES <- NA
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

---

```{r results = 'asis', echo=FALSE}
i = 219
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
file <- paste0("'", './images_evidence/', snp[,1],".png", "'")
cat("<img src=",file,"/>")
snp$CASES <- 6538
snp$CONTROLS <- 7363
snp$STAGE <- "1+2 | combined | scan + replication"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "flipped odd ratio | complementary RAF"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

---

```{r results = 'asis', echo=FALSE}
i = 220
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
file <- paste0("'", './images_evidence/', snp[,1], "_", snp[,8],".png", "'")
cat("<img src=",file,"/>")
snp$CASES <- 5504
snp$CONTROLS <- 4541
snp$STAGE <- "1"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "Due to missing allele frequencies for combined stage, first stage was considered"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)


i = 224
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
snp$CASES <- 5457
snp$CONTROLS <- 4492
snp$STAGE <- "1+2 | combined" 
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "The primary analysis was performed using logistic regression for genotype trend effect (with 1 degree of freedom) adjusted for study center, age and three eigenvectors (on the basis of principal-components analysis)"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)

i = 226
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
snp$CASES <- 6601
snp$CONTROLS <- 7433
snp$STAGE <- "1+2 | combined" 
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "flipped odd ratio | The primary analysis was performed using logistic regression for genotype trend effect (with 1 degree of freedom) adjusted for study center, age and three eigenvectors (on the basis of principal-components analysis)"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

---


```{r results = 'asis', echo=FALSE}
i = 221
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
file <- paste0("'", './images_evidence/', snp[,1], "_", snp[,8],".png", "'")
cat("<img src=",file,"/>")
snp$CASES <- 5505
snp$CONTROLS <- 4543
snp$STAGE <- "1"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "The primary analysis was performed using logistic regression for genotype trend effect (with 1 degree of freedom) adjusted for study center, age and three eigenvectors (on the basis of principal-components analysis)"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)

i = 223
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
snp$CASES <- 5450
snp$CONTROLS <- 4493
snp$STAGE <- "1"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "The primary analysis was performed using logistic regression for genotype trend effect (with 1 degree of freedom) adjusted for study center, age and three eigenvectors (on the basis of principal-components analysis)"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)

i = 225
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
snp$CASES <- 4066
snp$CONTROLS <- 4422
snp$STAGE <- "1"
snp$CLINICAL.VARIABLES <- NA
snp$NOTES <- "flipped odd ratio | complementary RAF | The primary analysis was performed using logistic regression for genotype trend effect (with 1 degree of freedom) adjusted for study center, age and three eigenvectors (on the basis of principal-components analysis) | adenocarcinoma cancer cases only"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

---

```{r results = 'asis', echo=FALSE}
i = 238
snp <- assoc[i,]
cat("#", as.character(snp[,8]), "|", as.character(snp[,4]))
```
> After excluding SNPs not present on the HumanHap 550v3 chip used
for the control samples, the final data set comprised 491,238
autosomal markers from 597 cases and 1295 control subjects.
This number of SNPs corresponds to 79% of the 620,901 SNPs
genotyped per patient.
> The replication sample consisted of 409 inpatients (179 men, 230 women) and
541 German control subjects matched to provide an equivalent
distribution of age and sex

```{r results = 'asis', echo=FALSE}
file <- paste0("'", './images_evidence/', snp[,1], ".png", "'")
cat("<img src=",file,"/>")
snp$CASES <- 597 + 409
snp$CONTROLS <- 1295 + 541
snp$STAGE <- "1 + 2 | combined | study + replication"
snp$CLINICAL.VARIABLES <- "Working memory task | Implicit emotion recognition task | Reward anticipation task | Functional magnetic resonance imaging (fMRI)"
snp$NOTES <- "Sum of study cohort and replication individuals to get sample sizes for controls and cases"
snp[,c("Sensitivity", "Specificity", "A", "B", "C", "D")] <- SenSes(snp)
kable(t(snp[,!(names(snp) %in% c("A", "B","CASES", "C", "D", "CONTROLS"))]))
snp -> assoc[i,]
contingency_table(snp)
```

---

# Sensitivity - Specificity plot

```{r}
curated_gwas <- subset(assoc, !is.na(CASES))

senses <- SenSes(
    curated_gwas[,c('CASES', 'CONTROLS', 'RISK.ALLELE.FREQUENCY', 'ORorBETA')]
    )

curated_gwas_senses <- cbind(curated_gwas, senses)
# plot(curated_gwas_senses$Specificity, curated_gwas_senses$Sensitivity,
#      main = "Specificity vs. Sensitivity for GWA studies",
#      xlab = "1- Specificity", ylab = "Sensitivity", xlim = c(0, 1), ylim = c(0, 1))
# text(curated_gwas_senses$Specificity, curated_gwas_senses$Sensitivity, 
#       row.names(curated_gwas_senses), cex=0.6, pos=4, col="blue")
# # text(1- curated_gwas_senses$Specificity, curated_gwas_senses$Sensitivity, 
# #      curated_gwas_senses$RISK.ALLELE.FREQUENCY, cex=0.6, pos=1, col="blue")
# abline(0, 1, col = "red", lty=2)


```


```{r chart, results='asis', comment = NA}
library('rCharts')
dP <- dPlot(
  Sensitivity ~ Specificity,
  groups = c("SNPS","RISK.ALLELE.FREQUENCY", "P.VALUE", "ORorBETA", "DISEASE.TRAIT"),
  data = curated_gwas_senses,
  type = "bubble",
  height = 650,
  width = 800

)
dP$xAxis(type = "addMeasureAxis", overrideMax = 1, outputFormat = ".2f")
dP$yAxis(overrideMax = 1, outputFormat = ".2f")
dP$legend(
   x = 200,
   y = 10,
   width = 400,
   height = 20,
   horizontalAlign = "right"
   )

dP$setTemplate(
  afterScript = sprintf(
'<script>
var line = d3.svg.line()
  .x(function(d) { return myChart.axes[0]._draw.scale()(d.x); })
  .y(function(d) { return myChart.axes[1]._draw.scale()(d.y); });

d3.select("#%s svg g")
  .append("path")
  .datum([{x:myChart.axes[0]._min,y:0},{x:myChart.axes[0]._max,y:1}])
  .attr("d",line)
  .style("stroke", "red")
  .style("stroke-width",0.5)
  .style("stroke-dasharray", "2");
</script>
',
dP$params$dom
))

dP$save('specificity-sensitivity_plot.html', cdn = TRUE)
cat('<a href=specificity-sensitivity_plot.html> specificity-sensitivity plot</a>')
```

---

```{r reproducibility}
# Ensure reproducibility
options(width = 120)
devtools::session_info()

```
